---
title: "My answers"
author: "Rachel Coxhead"
date: "2026-03-02"
output: html_document
---


```{r}
# Write your answer here
```


#### Summary Statistics

(@) Consider the `mtcars` dataset. Compare the average miles per gallon between 4 and 8 cylinders.

```{block, box.title = "Tip", box.body = list(fill = "lightblue")}
See the description of the dataset and find how to extract each variable.
```


```{r}
# Write your answer here
```


(@) Compare the summary statistics between the different transmissions.

```{r}
# Write your answer here
```


(@) For the miles per gallon and weights, which one has more variation?

```{r}
# Write your answer here
```


#### Plots

(@) Make the barplot for the number of cars with different transmissions.

```{r}
# Write your answer here
```


(@) What is the best way to see the distribution of cars by number of cylinders?

```{r}
# Write your answer here
```


(@) Find the summary statistics for weights and see if they agree with the information obtained from the boxplot.

```{r}
# Write your answer here
```


#### Further practice

You can practice more with built-in datasets in `R`. To find other datasets, type `data()` in the console to see more available datasets for you to try.
